---
title: "Real data application"
author: "Annachiara Rossi"
date: "9/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(Matrix)
library(roahd)
library(here) # to get the project directory
```

```{r}
data('mfD_healthy', package = 'roahd')
univariate_fdata <- mfD_healthy$fDList[[1]] # I consider the first lead only
plot(univariate_fdata)
```

# Non-adjusted functional boxplot

```{r, cache=TRUE}
fbp <- invisible(fbplot(univariate_fdata, main=""))
names(fbp$ID_outliers) = NULL
print(fbp$ID_outliers)
```

# Adjusted functional boxplot, roahd implementation (OGK_Qn)

```{r, cache=TRUE}
set.seed(130298)
fbp_roahd <- fbplot(univariate_fdata, main="", adjust = list(VERBOSE=FALSE))
invisible(fbp_roahd)

names(fbp_roahd$ID_outliers) = NULL
print(fbp_roahd$ID_outliers)
print(paste('Number of outliers: ',length(fbp_roahd$ID_outliers)))
```


# Remove extreme cases and contaminate with non-healthy patients

```{r}
extreme_obs <- fbp_roahd$ID_outliers
new_values <- univariate_fdata$values[-extreme_obs,]
# NB: the subscripting of fData objects doesn't work with negative indexes
grid <- seq(from = univariate_fdata$t0, to = univariate_fdata$tP, length.out = univariate_fdata$P)
data <- fData(grid, new_values)

plot(data)
```

Now contaminate this data with the same lead observed from subjects affected by Left-Bundle-Branch-Block.

```{r}
data('mfD_LBBB', package = 'roahd')
anomalies <- mfD_LBBB$fDList[[1]] # I consider the first lead only
plot(anomalies)
```

Sample a few observations from this data. Since we are left with 34 good samples, we can take 6 from the bad ones.

```{r}
set.seed(130298)
n_out <- 6
idx <- sample.int(anomalies$N, n_out)
# 10
idx <- c(3,35,2,16,31,48)
contamined_data <- append_fData(data, anomalies[idx])
out_highlighter <- rep(c(1,2),c(40-n_out,n_out)) 
plot(contamined_data, col=out_highlighter, 
     main ="ECG contamined data", cex.main =1,
     xlab = 'registered time (ms)', ylab = 'ECG lead I')
```


# Spot outliers

## Case without adjustment

```{r, cache=TRUE}
time_start = Sys.time()
fbp <- fbplot(contamined_data, main="Functional boxplot without adjustment", 
              cex.main = 1, xlab = 'registered time (ms)', ylab = 'ECG lead I')
time_end = Sys.time()
invisible(fbp)

names(fbp$ID_outliers) = NULL
print(fbp$ID_outliers)
print(paste('Number of outliers: ',length(fbp$ID_outliers)))
difftime(time_end, time_start, units = 'mins')[[1]]
``` 

TP = 4
FP = 0

## Cases with adjustment

```{r}
# get functional boxplot implementation from the project directory
source(here('user_fbplot.R'), chdir= TRUE)
```

### Ledoit_Wolf

```{r}
cov_estimator <- 'Ledoit_Wolf'
time_start = Sys.time()
fbp_lw <- my_fbplot.fData(contamined_data, 
                            main = cov_estimator, 
                            adjust = list(Cov_estimator = cov_estimator,
                                          TPR=2 * stats::pnorm( 4 * stats::qnorm( 0.15 ) )), 
                          cex.main = 1, 
                           xlab = 'registered time (ms)', 
                           ylab = 'ECG lead I')
time_end = Sys.time()
invisible(fbp_lw)

names(fbp_lw$ID_outliers) = NULL
print(fbp_lw$ID_outliers)
print(paste('Number of outliers: ',length(fbp_lw$ID_outliers)))
difftime(time_end, time_start, units = 'mins')[[1]]
```

TP = 5
FP = 6

### OGK-Qn

```{r, cache=TRUE}
time_start = Sys.time()
fbp_roahd <- fbplot(contamined_data, main="", adjust = list(VERBOSE=FALSE))
time_end = Sys.time()
invisible(fbp_roahd)

names(fbp_roahd$ID_outliers) = NULL
print(fbp_roahd$ID_outliers)
print(paste('Number of outliers: ',length(fbp_roahd$ID_outliers)))
difftime(time_end, time_start, units = 'mins')[[1]]
```

TP = 5
FP = 8



```{r}
cov_estimator <- 'OGK_Qn'
time_start = Sys.time()
fbp_ogk <- my_fbplot.fData(contamined_data, 
                            main = cov_estimator, 
                            adjust = list(Cov_estimator = cov_estimator,
                                          TPR=2 * stats::pnorm( 4 * stats::qnorm( 0.15 ) )), 
                           cex.main = 1, 
                           xlab = 'registered time (ms)', 
                           ylab = 'ECG lead I')
time_end = Sys.time()
invisible(fbp_ogk)

names(fbp_ogk$ID_outliers) = NULL
print(fbp_ogk$ID_outliers)
print(paste('Number of outliers: ',length(fbp_ogk$ID_outliers)))
difftime(time_end, time_start, units = 'mins')[[1]]
```

TP = 6
FP = 5

```{r}
cov_estimator <- 'MRCD'
time_start = Sys.time()
fbp_mrcd <- my_fbplot.fData(contamined_data, 
                            main = cov_estimator, 
                            adjust = list(Cov_estimator = cov_estimator,
                                          TPR=2 * stats::pnorm( 4 * stats::qnorm( 0.15 ) )),
                           cex.main = 1, 
                           xlab = 'registered time (ms)', 
                           ylab = 'ECG lead I')
time_end = Sys.time()
invisible(fbp_mrcd)

names(fbp_mrcd$ID_outliers) = NULL
print(fbp_mrcd$ID_outliers)
print(paste('Number of outliers: ',length(fbp_mrcd$ID_outliers)))
difftime(time_end, time_start, units = 'mins')[[1]]
```
TP = 6
FP = 7

I took L=P and computed eigenfunctions/eigenvalues. First 10 eigenvalues represent 18\% of variability, first 50 give 53\% and first 100 give 75\%.
L = 200 v = 0.88


```{r, message=FALSE, warning=FALSE}
cov_estimator <- 'Spherical'
time_start = Sys.time()
fbp_sph <- my_fbplot.fData(contamined_data, 
                            main = cov_estimator, 
                            adjust = list(Cov_estimator = cov_estimator,
                                          TPR=2 * stats::pnorm( 4 * stats::qnorm( 0.15 ) )), L = 100,
                           cex.main = 1, 
                           xlab = 'registered time (ms)', 
                           ylab = 'ECG lead I')
time_end = Sys.time()

names(fbp_sph$ID_outliers) = NULL
print(fbp_sph$ID_outliers)
print(paste('Number of outliers: ',length(fbp_sph$ID_outliers)))
difftime(time_end, time_start, units = 'mins')[[1]]
```

TP = 6
FP = 9

```{r, message=FALSE, warning=FALSE}
cov_estimator <- 'Median'
time_start = Sys.time()
fbp_med <- my_fbplot.fData(contamined_data, 
                            main = cov_estimator, 
                            adjust = list(Cov_estimator = cov_estimator,
                                          TPR=2 * stats::pnorm( 4 * stats::qnorm( 0.15 ) )), L = 100,
                           cex.main = 1, 
                           xlab = 'registered time (ms)', 
                           ylab = 'ECG lead I')
time_end = Sys.time()

names(fbp_med$ID_outliers) = NULL
print(fbp_med$ID_outliers)
print(paste('Number of outliers: ',length(fbp_med$ID_outliers)))
difftime(time_end, time_start, units = 'mins')[[1]]
```

TP = 6
FP = 10


```{r, message=FALSE, warning=FALSE}
cov_estimator <- 'Kendall'
time_start = Sys.time()
fbp_ken <- my_fbplot.fData(contamined_data, 
                            main = cov_estimator, 
                            adjust = list(Cov_estimator = cov_estimator,
                                          TPR=2 * stats::pnorm( 4 * stats::qnorm( 0.15 ) )),
                           cex.main = 1, 
                           xlab = 'registered time (ms)', 
                           ylab = 'ECG lead I')
time_end = Sys.time()

names(fbp_ken$ID_outliers) = NULL
print(fbp_ken$ID_outliers)
print(paste('Number of outliers: ',length(fbp_ken$ID_outliers)))
# doesn't work because of bandwidth ??
difftime(time_end, time_start, units = 'mins')[[1]]
```









